---
title: "WWD assignment 2"
author: "zhou ziliang"
date: "2019/10/17"
output:
  html_document:
    df_print: paged
---
# Course Work 2

1. Load the file into RStudio

```{r load file, message=FALSE, cache=TRUE}
library(tidyverse)
animals <- read.csv("Animals.csv")  
```

2. Rename (use the "rename" function) the "x" variable to "Weight", the "y" variable to "Height" and the"z" variable "Species"

```{r Rename,cache=TRUE}
animals <- rename(animals,Weight = "x",Height = "y", Specise = "z")
```

3. Rename the levels of "Species": a=Ostrich, b=Deer, c= Bear, d= Giant tortoise 

```{r Rename specise,cache=TRUE}
animals$Specise <- factor(animals$Specise, levels = c("a","b","c","d"),
                          labels = c("Ostrich","Deer","Bear","Gaint tortise"))
```

4. Use "mutate" to create a new variable called BMI 

```{r BMI, cache=TRUE}
animals <- mutate(animals,BMI = animals$Weight/animals$Height^2) 
```

5. Create a scatter plot to explore the relationship between Height and Weight. 

  answer: I cannot find obverse relationship between weight and hight
```{r echo=TRUE}
ggplot(animals, aes(x=Weight,y=Height))+
  geom_point()
```

6. Create a scatter plot to explore the relationship between Height and Weight split by species 

  answer: weight and height are positively correlated in the same species
```{r echo=TRUE}
ggplot(animals, aes(x= Weight,y = Height))+
  geom_point()+
  facet_grid(~Specise,)
```

7. Use an appropriate graph to explore the BMI of the different species types.


```{r}
ggplot(animals,aes(x = Specise,y = BMI))+
  geom_boxplot(fill = 'wheat',color = 'black')
```